\documentclass[letterpaper, 9pt]{extarticle}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}
\usepackage{newtxtext,newtxmath}
\usepackage{merriweather}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\Large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\definecolor{darktext}{rgb}{0.1, 0.1, 0.1}

\color{darktext}

% Adjust itemize settings
\setlist[itemize]{leftmargin=*}

\begin{document}

\begin{center}
	\textbf{{\Huge SAI SURYA SIVA PRASAD RAGHAVARAPU}}
\end{center}

\begin{center}
{\faGithub} \href{https://github.com/sai-surya-siva-prasad}{GitHub} |
{\faLinkedin} \href{https://linkedin.com/in/siyasurya}{LinkedIn} |
{\faBriefcase} \href{https://taupe-mousse-8028fd.netlify.app/}{Portfolio} |
{\faEnvelopeO} \href{mailto:suryaraghavarapu@gmail.com}{Email} |
{\faPhone} \href{tel:+17405520627}{+1 7405520627}
\end{center}

\section{Introduction}
Experienced full stack developer skilled in building scalable web applications and passionate about data-driven insights. Excited to combine expertise in full stack development and data science to drive innovation. Seeking opportunities to contribute to transformative projects and make a meaningful impact.

\section{Education}
\begin{itemize}
\item \textbf{MS in Computer Science} | Rutgers University, New Brunswick (NB) | 2024 | GPA: 3.6
\item \textbf{B.Tech in Electronics and Communication Engineering} | Amrita University, Bangalore | 2020 | GPA: 3.6
\end{itemize}

\section{Experience}
\begin{itemize}
\item \textbf{Accenture, Software Engineer, 2020-2022}
\begin{itemize}
    \item Engineered and deployed Salesforce Document Auto-Fill feature leveraging Apex triggers, classes, and Amazon Textract, resulting in a 50\% reduction in document processing time while ensuring impeccable data accuracy.

      \item Integrated Salesforce with Amazon Textract, achieving a 50\% reduction in processing time and ensuring seamless OCR and text extraction for improved efficiency.

    \item Designed, developed, and deployed the "Near By Healthcare Professionals" feature, integrating Salesforce Maps API, Apex controllers, and Lightning Web Components within the patient portal, leading to a 40\% reduction in search time for healthcare professionals.
    \item Developed and deployed a custom Apex trigger, resulting in a 30\% reduction in manual effort for calculating due dates across the organization's global Salesforce system.
    \item Implemented time zone handling and utilized custom objects/settings to manage holiday schedules, improving due date accuracy by 95\% and enhancing productivity for teams working in different regions.
\end{itemize}
\item \textbf{Experts Hub, Software Engineer, 2019-2020}
\begin{itemize}
    \item Developed and deployed Salesforce Apex controllers and Lightning Web Components to consume the Google News API through REST calls, enabling real-time healthcare news updates within the patient portal.
    \item Improved user engagement metrics with a notable 40\% increase in daily active users and a substantial 25\% boost in average session duration, enhancing patient satisfaction and information accessibility.
    \item Developed Salesforce Voice Integration with Amazon Alexa API, Apex controllers, and Lightning Web Components, improving healthcare professionals' efficiency by 40\% in initiating voice calls to patients.
   \item Implemented real-time speech-to-text feature with continuous translation using the industry-leading Google Cloud Speech-to-Text API, resulting in a 40\% reduction in manual data entry time for healthcare professionals.
\end{itemize}
\end{itemize}

\section{Projects}
\begin{itemize}[leftmargin=*]
\item \textbf{Full-Stack Development of a GPT-Integrated Blogging Platform with Next.js} | April 2023 - June 2022 

\begin{itemize}
\item Built a comprehensive blogging platform using Next.js 13.3, Prisma, TipTap, and TypeScript, focusing on efficient data handling, user-friendly interfaces, and robust server-side rendering,resulting in a 50\% increase in site performance and a 30% improvement in load times.
\item  Integrated OpenAI's ChatGPT for automated blog post creation, leading to a 40\% increase in content production and a 20\% increase in user engagement. Successfully deployed the application on Vercel, supporting over 10,00 active users.
\end{itemize}

\item \textbf{MERN Finance Dashboard App with Machine Learning Predictions} | Rutgers University | January 2023 - March 2023 

\begin{itemize}
\item Developed a finance dashboard application with machine learning predictions, improving financial data analysis and decision-making processes.
\item Enhanced user experience and data visualization by implementing Material UI and Recharts, and improved state management with Redux Toolkit.
\end{itemize}

\item \textbf{Fullstack MERN Social Media Application with Authentication, Likes, and Dark Mode} | September 2022 - December 2022 

\begin{itemize}
\item Developed a Fullstack MERN Social Media Application, integrating complex features such as user authentication, post creation, and dark mode. Optimized the application's performance by 25\% through efficient code practices and database management.
\item Leveraged Material UI for a responsive design and Redux for efficient state management. Improved the application's load time by 15\% by optimizing React components and implementing efficient Redux actions and reducers.
\end{itemize}
\end{itemize}

\section{Skills}
\begin{itemize}
\item \textbf{Front end}: Next.js, React.js, HTML, CSS, JavaScript
\item \textbf{Backend}: Node.js, Express.js, MongoDB, Firebase
\item \textbf{Languages}: JavaScript, Python, Java, C++
\item \textbf{Technologies}: Salesforce, Apex, Lightning Web Components, Amazon Web Services (AWS), Google Cloud Platform (GCP), RESTful APIs
\item \textbf{Other}: Git, Agile/Scrum, UI/UX Design
\end{itemize}

\end{document}
